---
title: "Site 2 Classifier Comparison"
author: "Natalie"
date: "2024-08-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages}
library(mlr3)
library(mlr3learners)
library(mlr3spatial)
library(terra)
library(sf)
library(ggplot2)
library(tidyterra)
library(here)
```

```{r}
site2 <- rast(here("Data", "sites_1.3cm_cropped", "site2_cropped", "site2_cropped.tif"))
names(site2) <- c("Band_1", "Band_2", "Band_3")
plotRGB(site2)
site2_pts <- read_sf(here("Data", "sites_1.3cm_cropped", "site2_cropped", "site2_cropped_pts_rgb.gpkg"), stringsAsFactors = T)
site2_pts <- select(site2_pts, -rand_point)
site2_pts
```
Create spatial task
```{r}
site2_tsk <- as_task_classif_st(site2_pts, target = "className")
```

Partition data
```{r}
set.seed(102)
site2_split <- partition(site2_tsk, ratio = 0.7)
```

Create learner
```{r}
site2_lrn <- lrn("classif.ranger")
```

Train learner
```{r}
site2_train <- site2_lrn$train(site2_tsk, site2_split$train)
```

Test learner and obtain classification accuracy
```{r}
#use learner to predict on the test partition of the task
site2_test <- site2_lrn$predict(site2_tsk, site2_split$test)

#obtain classification accuracy
site2_test$score(msr("classif.acc"))
```

# Apply the site2 model on other sites and obtain its classification accuracy

Import the point data from all sites, each containing an associated class. We will use this to obtain classification accuracy but comparing the class the model has classifed the point has, versus what class the point actually is. 
```{r}
site1_pts <- read_sf(here("Data", "sites_1.3cm_cropped", "site1_cropped", "site1_cropped_pts.shp"))
site3_pts <- read_sf(here("Data", "sites_1.3cm_cropped", "site3_cropped", "site3_cropped_pts.shp"))
site4_pts <- read_sf(here("Data", "sites_1.3cm_cropped", "site4_cropped", "site4_cropped_pts.shp"))
site5_pts <- read_sf(here("Data", "sites_1.3cm_cropped", "site5_cropped", "site5_cropped_pts.shp"))
site6_pts <- read_sf(here("Data", "sites_1.3cm_cropped", "site6_cropped", "site6_cropped_pts.shp"))
site7_pts <- read_sf(here("Data", "sites_1.3cm_cropped", "site7_cropped", "site7_cropped_pts.shp"))
```

Import the rasters of all sites
```{r}
site1_rast <- rast(here("Data", "sites_1.3cm_cropped", "site1_cropped", "site1_cropped.tif"))
site3_rast <- rast(here("Data", "sites_1.3cm_cropped", "site3_cropped", "site3_cropped.tif"))
site4_rast <- rast(here("Data", "sites_1.3cm_cropped", "site4_cropped", "site4_cropped.tif"))
site5_rast <- rast(here("Data", "sites_1.3cm_cropped", "site5_cropped", "site5_cropped.tif"))
site6_rast <- rast(here("Data", "sites_1.3cm_cropped", "site6_cropped", "site6_cropped.tif"))
site7_rast <- rast(here("Data", "sites_1.3cm_cropped", "site7_cropped", "site7_cropped.tif"))

#rename layers to Band_1, Band_2 and Band_3
site_ids <- setdiff(1:7, 2)
for (site_id in site_ids) {
  raster <- get(paste0("site", site_id, "_rast"))
  names(raster) <- c("Band_1", "Band_2", "Band_3")
  assign(paste0("site", site_id, "_rast"), raster)
  print(paste("Renamed layers for site", site_id))
}
```


Create list of site ids
```{r}
site_ids <- setdiff(1:7, 2) 
```

Create vector to store accuracy results
```{r}
accuracy_results <- numeric(length(site_ids))
names(accuracy_results) <- paste0("site_", site_ids)
```

Create loop over each site excluding site 2
```{r}
for (i in seq_along(site_ids)) {
  site_id <- site_ids[i]
  raster_to_classify <- get(paste0("site", site_id, "_rast"))
  points_shapefile <- get(paste0("site", site_id, "_pts"))
  classified_raster <- predict_spatial(raster_to_classify, site2_lrn)
  extracted_values <- extract(classified_raster, points_shapefile)
  raster_className <- extracted_values[,2]
  shapefile_className <- points_shapefile$className
  accuracy_vector <- raster_className == shapefile_className
  classification_accuracy <- sum(accuracy_vector) / length(accuracy_vector)
  accuracy_results[i] <- classification_accuracy
  print(paste("Classification Accuracy for Site", site_id, ":", classification_accuracy))
}
```

Print final classification accuracy output
```{r}
print(accuracy_results)
```


